Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-27 LatexNotes/Notes.tex
NM

The KdV equation in dimensional form is
\begin{equation}
2 \eta_t + \frac{3 c}{h_0} \eta \eta_{\xi} + \frac{c h_0^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
Here, $\eta$ has units of length, $t$ time, $c = \sqrt{g h_0}$ is the wave speed, and $\xi = x - ct$. I obtained this equation by starting from Johnson's dimensionless equation ()

\subsubsection{Johnson's formulation}
Following Johnson's derivation, the dimensionless KdV equation is (on page 208)
\begin{equation}
2 \eta_{\tau} + 3 \eta \eta_{\xi} + \frac{1}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
I had to work backwards quite a bit to figure out how this was non-dimensionalized (Johnson keeps rescaling things over and over again). Ultimately, the characteristic scales are
\begin{align}
& X^* = \eps^{-1/2} h_0 ,\quad T^* = \eps^{-1/2} \sqrt{h_0/g} , \quad \eta^* = \eps h_0, \\
& Z^* = h_0 , \quad U^* = \eps \sqrt{g h_0} , \quad W^* = \eps^{3/2} \sqrt{g h_0} , \quad P^* = \eps \rho g h_0
\end{align}
where $\eps$ is the ratio of characteristic amplitude to depth
\begin{equation}
\eps = a / h_0
\end{equation}
The variables $\tau$ and $\xi$ are
\begin{align}
\tau = \eps t , \quad \xi = x-t
\end{align}
Remember, the privileged KdV scaling is $\delta^2 \sim \eps$ where $\delta = h_0 / \lambda$. If this scaling is inserted into above, then $X^* \sim \lambda$, $T^* \sim \lambda/\sqrt{g h_0}$ which all makes sense.

>>>>

The KdV equation in dimensional form is
\begin{equation}
2 \eta_t + \frac{3 c}{h_0} \eta \eta_{\xi} + \frac{c h_0^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
Here, $\eta$ has units of length, $t$ time, $c = \sqrt{g h_0}$ is the wave speed, and $\xi = x - ct$. I obtained this equation by starting from Johnson's dimensionless equation (3.28) on page 208 and working backwards to untangle the scales that he had used to non-dimensionalize.

Let's establish some basic scales and notation:
% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}[h]%[htbp]
\begin{center}
\caption{Table.}
\label{scale_table}
\begin{tabular}{l l l l}
\hline Description & Notation & Upstream  value \,\, & Downstream value \\
\hline
Characteristic wave amplitude	& $a = \etastd = \mean{\eta^2}^{1/2}$	& varied	& varied \\
Peak forcing frequency		& $f_p$				& 2 Hz		& N/A \\
Depth					& $h_0^{\pm}$			& 12.5 cm		& 3 cm \\
Peak wavelength			& $\lambda_p^{\pm}$	& 38 cm		& 25 cm \\
%Peak wavenumber			& $k_p$				& 0.17 rad/cm	& 0.25 rad/cm \\
%Dimensionless depth			& $k_p h$				& 2.1		& 0.76
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

\vsp{10}
\subsubsection{Johnson's formulation}
Following Johnson's derivation, the dimensionless KdV equation is (on page 208)
\begin{equation}
2 \eta_{\tau} + 3 \eta \eta_{\xi} + \frac{1}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
I had to work backwards quite a bit to figure out how this was non-dimensionalized (Johnson keeps rescaling things over and over again). Ultimately, the characteristic scales are
\begin{align}
& X^* = \eps^{-1/2} h_0 ,\quad T^* = \eps^{-1/2} \sqrt{h_0/g} , \quad \eta^* = \eps h_0, \\
& Z^* = h_0 , \quad U^* = \eps \sqrt{g h_0} , \quad W^* = \eps^{3/2} \sqrt{g h_0} , \quad P^* = \eps \rho g h_0
\end{align}
where $\eps$ is the ratio of characteristic amplitude to depth
\begin{equation}
\eps = a / h_0
\end{equation}
The variables $\tau$ and $\xi$ are
\begin{align}
\tau = \eps t , \quad \xi = x-t
\end{align}
Remember, the privileged KdV scaling is $\delta^2 \sim \eps$ where $\delta = h_0 / \lambda$. If this scaling is inserted into above, then $X^* \sim \lambda$, $T^* \sim \lambda/\sqrt{g h_0}$ which all makes sense.
